Discovery of s-process stars in the LAMOST survey

### 2018-01-24 article/ms.tex
add schlauf affil and spacing for author initials

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

@@

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[B.J. Norfolk et al.]{B.J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
A.R. Casey,$^{1,2}$
M.T. Miles,$^{1}$
A.J. Kemp,$^{1}$ 
A.I. Karakas,$^{1}$ \newauthor
J.C. Lattanzio,$^{1}$
and K.C. Schlaufman 
\\
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
}
\date{Accepted XXX. Received YYY; in original form ZZZ}

>>>>

@@

\author[B.~J. Norfolk et al.]{B.~J. Norfolk,$^{1}$\thanks{E-mail: bjee7@student.monash.edu (MU)}
A.~R. Casey,$^{1,2}$
M.~T. Miles,$^{1}$
A.~J. Kemp,$^{1}$ 
A.~I. Karakas,$^{1}$ \newauthor
J.~C. Lattanzio,$^{1}$
and K.~C. Schlaufman$^{3}$
\\
$^{1}$School of Physics \& Astronomy, Monash University, Clayton 3800, Victoria, Australia\\
$^{2}$Faculty of Information Technology, Monash University, Clayton 3800, Victoria, Australia\\
$^{3}$Department of Physics and Astronomy, Johns Hopkins University, 3400 N Charles St., Baltimore, MD 21218, USA
}
\date{Accepted XXX. Received YYY; in original form ZZZ}
